### 2021-11-21 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@660240bf6e3b4134bf60bcd6197afeb33838ee85 🚀

Interactions between plants and pollinators form networks of
interactions, which structure the ``architecture of biodiversity''
(\textbf{Jordano2007?}). The functioning and stability of ecosystems
emerge from these interactions, but antropogenic change threatens to
unravel and ``rewire'' these networks (\textbf{CaraDonna2017IntRew?}),
threating the persistence of these systems. Plant-pollinator networks
face two possible forms of rewiring in response to anthropogenic
environmental change: spatial and temporal. Spatially, range shifts
could cause interacting species to no longer overlap in space, and
shifts in phenology could cause interacting species to no longer overlap
in time.

This chapter uses several years of data on bumblebee-flower phenology
and interactions across several field sites, each consisting of several
plots across an elevational gradient, combined with spatial records of
species occurrence via GBIF to forecast this uncoupling. This addresses
the EBV to forecast of EBV element of the flow from data to mitigation
in fig.~\ref{fig:thesis} (left).

\begin{figure}
\centering
\includegraphics{./figures/ch1.png}
\caption{chapter one concept fig}
\end{figure}

@@

The data for this chapter is derived from multiple souces and can be
split into four categories. (1) Field data from three different field
sites across Colorado, each with multiple plots across an elevational
gradient, for seven, seven, and three years resptively. This data was
collected by Paul CaraDonna and Jane Oglevie (from the Rocky Mountain
Biological Laboratory) and Julian Resasco (CU Boulder). (2) GBIF spatial
occurrence records of each of these species across Colorado, including a
metaweb of interactions across all of Colroado taken from GBIF. (3)
Remotely sensed data consisting of current and forecasting bioclimatic
variables from CHELSA. (4) Phylogeny derived from NCBI GenBank barcodes
for mitochondrial COI (bumblebees) and chloroplast rbcL (flowers).

@@

As the data we have is spatially sparse and likely to contain many
interaction ``false-negatives'' (Strydom \emph{et al.} 2021), we beign
by predicting a metaweb of interactions as they exist \emph{in the
present}.

In stages, (1) take data from multiple sites to predict a spatial
metaweb of \emph{Bombus}-flower interactions across Colorado. (2)
Predict how these spatial distributions will change under CMIP6. and (3)
quantify the lack of overlap between species for which there is a
predicted

The process of going from data to forecast can be split into the
following parts

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Building an interaction prediction model (or rather a set of candidate
  models, relative abundance, phylo embedding relative abundance + phylo
  embedding) a la Strydom \emph{et al.} (2021)
\end{enumerate}

Reconstructing latent features for each species based on simulating
trait evolution on a phylogeny (\textbf{Strydom2021FooWeb?}).

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\setcounter{enumi}{1}
\item
  Make it spatial based on distributions.
\item
  Forecast distributions based on CMIP6
\end{enumerate}

@@

@@

This chapter uses simulation models to investigate the relationship
between species relative abundance, sampling effort, and probability of
accurately detecting an interaction between species, and further
proposes a method for optimizing the spatial sampling locations to
maximize the probability of detecting an interaction between two species
given their distributions. This addresses the optimization of monitoring
network part of the flow from data to mitigation in
fig.~\ref{fig:thesis}.

As explored in the previous chapter, there are false-negatives in
interation data. There is more than one way to observe a false-negative
when sampling interactions: (fig.~\ref{fig:fnrtaxonomy}). It begins with
a conceptual framework for understanding the difference in
false-negatives in occurrence, co-occurrence, and interactions.
Co-occurrence is not the same thing as interaction (Blanchet \emph{et
al.} 2020), but often is used as a proxy.

\begin{figure}
\hypertarget{fig:fnrtaxonomy}{%
\centering
\includegraphics{./figures/ch2.png}
\caption{taxonomy of false negatives}\label{fig:fnrtaxonomy}
}
\end{figure}

We use a log-normal distribution as a null model of the
relative-abundance distribution (Hubbell 2001) to simulate realized
false-negative rate as a function of varying sampling effort.

>>>>

Interactions between plants and pollinators form networks of
interactions, which together create the ``architecture of biodiversity''
(\textbf{Jordano2007?}). The functioning and stability of ecosystems
emerge from these interactions, but anthropogenic change threatens to
unravel and ``rewire'' these interaction networks
(\textbf{CaraDonna2017IntRew?}), threatening the persistence of these
systems. Plant-pollinator networks face two possible forms of rewiring
in response to anthropogenic environmental change: spatial and temporal.
Spatially, range shifts could cause interacting species to no longer
overlap in space, and shifts in phenology could cause interacting
species to no longer occur at the same time of year. This chapter uses
several years of data on bumblebee-flower phenology and interactions
across several field sites, each consisting of several plots across an
elevational gradient, combined with spatial records of species
occurrence via GBIF to forecast this uncoupling. This addresses the EBV
to forecast element of the flow from data to mitigation in
fig.~\ref{fig:thesis} (left).

\begin{figure}
\centering
\includegraphics{./figures/ch1.png}
\caption{Chapter One conceptual figure. Left: the sources of data and
how they can be synthesized. Right: The flow from data to interaction
prediction using a few different interaction prediction models.}
\end{figure}

@@

The data for this chapter is derived from multiple sources that can be
split into four categories. (1) Field data from three different field
sites across Colorado, each with multiple plots across an elevational
gradient, for seven, seven, and three years respectively. This data was
collected by Paul CaraDonna and Jane Oglevie (from the Rocky Mountain
Biological Laboratory; RMBL) and Julian Resasco (CU Boulder). (2) GBIF
spatial occurrence records of each of these species across Colorado,
including a metaweb of interactions across all of Colroado taken from
GBIF. (3) Remotely sensed data consisting of current and forecasting
bioclimatic variables from CHELSA. (4) Phylogenies for both bee and
flower species derived from NCBI GenBank barcodes for mitochondrial COI
(bumblebees) and chloroplast rbcL (flowers).

@@

As the data we have is spatially sparse and likely to contain many
interaction ``false-negatives'' (Strydom \emph{et al.} 2021), we begin
by predicting a metaweb of interactions across Colorado as they exist
\emph{in the present}. We do this using a set of candidate interaction
prediction models: relative abundance only, phylogenetic embedding only
(a la (\textbf{Strydom2021FooWeb?})), niche embedding only
(\textbf{Gravel2019BriElt?}), and all pairwise combinations of those
constituent models. After validating each model and selecting the best
performing model, we then predict how these distributions of each of
these species will change under the CMIP6 consensus climate forecast
{[}@{]}, and then finally quantify the reduction in spatial between
species for which there is a predicted interaction.

@@

\hypertarget{next-steps}{%
\subsection{Next steps}\label{next-steps}}

@@

This chapter uses simulation models to investigate the relationship
between species relative abundance, sampling effort, and probability of
accurately detecting an interaction between species, and further
proposes a method for optimizing the spatial sampling locations to
maximize the probability of detecting an interaction between two species
given their distributions. This addresses the optimization of monitoring
network part of the flow from data to mitigation at the top of
fig.~\ref{fig:thesis}, left.

As explored in the previous chapter, there are false-negatives in
interaction data. However, there is more than one way to observe a
false-negative when sampling interactions: (fig.~\ref{fig:fnrtaxonomy}).
It begins with a conceptual framework for understanding the difference
in false-negatives in occurrence, co-occurrence, and interactions.
Co-occurrence is not the same thing as interaction (Blanchet \emph{et
al.} 2020), but often is used as a proxy.

\begin{figure}
\hypertarget{fig:fnrtaxonomy}{%
\centering
\includegraphics{./figures/ch2.png}
\caption{A taxonomy of occurrence, co-occurrence, and interaction false
negatives in data}\label{fig:fnrtaxonomy}
}
\end{figure}

We use a log-normal distribution as a null model of the
relative-abundance distribution (Hubbell 2001) and then simulate
realized false-negative rate as a function of varying sampling effort.
